Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2020-06-24 area_agg_seq_tsas.tex
improved citing
improved according to reviewers' comments

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
    {\protect\\ \Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

@@

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We have proved that this problem is NP-hard.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
We present the \Astar algorithm and integer linear programming
to solve this optimization problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm as a benchmark.
We tested the three methods with a
dataset of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
We believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

We consider CMG as the process of producing maps 
covering a continuous interval of scales,
where CMG considers constraints and quality measures 
that act across different scales. 
In our work, for example, the quality of an aggregation sequence 
is measured as a whole; 
whereas in classical generalization approaches, 
only the quality of a map at some output scale is measured.
We consider CMG possible, desirable, and realistic.
In CMG, it is not necessary that 
all changes that occur during zooming are animated in a continuous fashion. 
That fashion may generally be possible. 
A simple way is to fade in and fade out raster maps
as did by \textcite{Pantazis2009b}, 
but it is not at all clear 
whether such animations would improve the experience of the map user.
By contrast, we would like to carry out the changes in a more elegant way;
we would like to change map features gradually.

\mypar{Problem definition}
In this paper, we deal with CMG of land-cover areas.
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.

@@

We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence of land-cover maps.

Our method can also be extended to find an aggregation sequence 
for two maps (a start map and a goal map) that are from different sources.
In that case, one could compute a map overlay of the two maps
and use the result 
(with combined boundaries from both input maps and land cover classes 
from the given large-scale map) 
as the start map.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive at the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

@@

\mypar{Contribution}
We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether \Astar or the ILP-based algorithm, 
which are more complex and slower, indeed perform better.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

We do not deal with simplifying polylines in this paper.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
%
Although splitting polygons is a good step
of generalizing land-cover areas,
we do not integrate it into our method at this moment.
Some examples of splitting are as follows.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split tiny polygons 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on a constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.

@@

\emph{Continuous map generalization} (CMG)
has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
\caption{The numbers of regions where \Astar was 
	forced to use the given overestimation parameters
	in order to find a solution 
	without exploring more than 
	$W \in \{200{,}000;~400{,}000\}$ 
	nodes of the subdivision graph.}
\label{fig:AreaAgg_OverStats}
\end{figure}

@@

\begin{table*}[tb]
\caption{The costs in detail of some regions, 
	where~$W=200{,}000$.  
	Parameters~$n$ and~$m$ are the numbers of patches and 
	adjacencies on the start map, respectively.
	Parameter $K$ is the overestimation factor, 
	defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
	We evaluate the quality 
	of our estimations for type change and 
	compactness by listing the numbers~
	$R_\mathrm{type}=g_\mathrm{type}(\Pgoal)
	/h_\mathrm{type}(\Pstart)$ and~
	$R_\mathrm{comp}=g_\mathrm{comp}(\Pgoal)
	/h_\mathrm{comp}(\Pstart)$. 
	Note that if~$h_\mathrm{type}(\Pstart)=0$,
    then we have~$g_\mathrm{type}(\Pgoal)=0$; 
	in this case, we define~$R_\mathrm{type}=1$.
	The marked entries are discussed in the text.
}
\label{tab:CostsInDetail}
\centering
\includegraphics[page=3]{AreaAgg_CaseStudy1_Plot}
\end{table*}

@@

\section{Concluding Remarks}
\label{sec:AreaAgg_Conclusions}
In this paper, we investigated the problem of 
finding optimal sequences for area aggregation.
We compared three methods to solve this problem, namely, 
a greedy algorithm, \Astar, and an ILP-based algorithm.
The greedy algorithm is used as a benchmark.
Unsurprisingly, it ran faster than the other two methods by far.
According to our experiments, \Astar found area aggregation 
sequences
with the least total cost over all regions.
For some instances, however, \Astar had to overestimate
in order to find feasible solutions.
Compared to the greedy algorithm, 
\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
in the two experiments.
Although the amount is small, it is worth to use \Astar
because optimization methods can help us 
to evaluate the quality of a model 
\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
even an \emph{optimal} sequence can be bad.
If it were not for \Astar, 
we could not tell if the bad result was caused 
by the greedy algorithm or the model.
Because of \Astar, we are sure that the bad result is from
our model of minimizing the 
type change and the compactness.
The ILP-based algorithm finds optimal solutions for some regions,
but for some of the other regions 
it cannot even find a feasible solution.
Compared to the ILP-based algorithm,
\Astar used less memory 
yet found optimal solutions for more regions.

@@

\begin{acks}
We thank Thomas C. van Dijk, Joachim Spoerhase, 
and Sabine Storandt for their valuable suggestions.
We thank Martijn Meijers for 
prereviewing an earlier version of this paper.
\end{acks}

>>>>

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
    {\Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

@@

In each step of the \mine{computed} sequence, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We have proved that this problem is NP-hard.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
We present the \Astar algorithm and integer linear programming
to solve this optimization problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm as a benchmark.
We tested the three methods with a
dataset of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
We believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps \mine{with a smooth scale transition}
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} stated.
%We consider CMG as the process of producing maps 
%covering a continuous interval of scales,
%where CMG considers constraints and quality measures 
%that act across different scales. 
%In our work, for example, the quality of an aggregation sequence 
%is measured as a whole; 
%whereas in classical generalization approaches, 
%only the quality of a map at \mine{an} output scale is measured.
%We consider CMG possible, desirable, and realistic.
%In CMG, it is not necessary that 
%all changes that occur during zooming are animated in a continuous fashion. 
%That fashion may generally be possible.

A simple way \mine{of realizing CMG} is to fade in and fade out raster maps
as did by \textcite{Pantazis2009b}, 
but it is not at all clear 
whether such animations would improve the experience of map users.
\mine{Furthermore, although it is possible to generalize raster maps,
we consider it more straightforward to work on vector maps.
For example, \textcite{Jaakkola1998Generalization}
generalized raster maps, but he used essentially the same object-based operators 
that are common in the map generalization of vector data.
He even converted raster data to vector data
when he wanted to simplify the boundaries of the land-cover areas.
Therefore, our paper will work on a vector map of land-cover areas.}

%As , we would like to carry out the changes in a more elegant way;
%we would like to change map features gradually.

%He generalizes raster maps, using essentially the same object-based map generalization operators that are common in the generalization of vector data. I.e., patches consisting of pixels of equal land-cover types are considered as objects which can be merged with neighboring patches.

\mypar{Problem definition}
In this paper, we deal with CMG of land-cover areas.
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to \mine{aggregate the tiny areas} 
into their neighboring areas.

@@

We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the \mine{goal} map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence of maps.

Our method can also be extended to find an aggregation sequence 
for two maps (a start map and a goal map) that are from different sources.
In that case, one could compute a map overlay of the two maps
and use the result 
(with combined boundaries from both input maps and land cover classes 
from the given larger-scale map) 
as the start map.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive at the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014Support,vanOosterom2014tGAPSSC}.

@@

\mypar{Contribution}
We \mine{first} show \mine{some} related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether \Astar or the ILP-based algorithm, 
which are more complex and slower, indeed perform better.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

We do not deal with simplifying polylines in this paper.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
\mine{Note that simplifying polylines will not speed up 
our three algorithms.
The reason is that we compute the areas of the polygons 
and the lengths of the boundaries in a preprocessing.
These values will be associated with
a graph representation of the dataset, 
where polygons are represented as vertices and 
a boundary separating two polygons (no matter how detailed it is) 
is represented with a single edge.
During computation, the three algorithms do not need to go through 
the vertices of the land-cover areas.
}

Although splitting polygons is a good step
of generalizing land-cover areas,
we do not integrate it into our method at this moment.
Some examples of splitting are as follows.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split tiny polygons 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on a constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors;
when merging, a more attractive neighbor 
will get a larger portion from the splittee.

@@

\emph{Continuous map generalization} (CMG)
has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014Support} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_CaseStudy1_Plot}
\caption{The numbers of regions where \Astar was 
	forced to use the given overestimation parameters
	in order to find a solution 
	without exploring more than 
	$W \in \{200{,}000;~400{,}000\}$ 
	nodes of the subdivision graph.}
\label{fig:AreaAgg_OverStats}
\end{figure}

@@

\begin{table*}[tb]
\caption{The costs in detail of some regions, 
	where~$W=200{,}000$.  
	Parameters~$n$ and~$m$ are the numbers of patches and 
	adjacencies on the start map, respectively.
	Parameter $K$ is the overestimation factor, 
	defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
	We evaluate the quality 
	of our estimations for type change and 
	compactness by listing the numbers~
	$R_\mathrm{type}=g_\mathrm{type}(\Pgoal)
	/h_\mathrm{type}(\Pstart)$ and~
	$R_\mathrm{comp}=g_\mathrm{comp}(\Pgoal)
	/h_\mathrm{comp}(\Pstart)$. 
	Note that if~$h_\mathrm{type}(\Pstart)=0$,
    then we have~$g_\mathrm{type}(\Pgoal)=0$; 
	in this case, we define~$R_\mathrm{type}=1$.
	The marked entries are discussed in the text.
}
\label{tab:CostsInDetail}
\centering
\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
\end{table*}

@@

\section{Concluding Remarks}
\label{sec:AreaAgg_Conclusions}
In this paper, we investigated the problem of 
finding optimal sequences for area aggregation.
We compared three methods to solve this problem, namely, 
a greedy algorithm, the \Astar algorithm, and an ILP-based algorithm.
The greedy algorithm is used as a benchmark.
Unsurprisingly, it ran faster than the other two methods by far.
According to our experiments, \Astar found area aggregation sequences
with the least total cost over all regions.
For some instances, however, \Astar had to overestimate
in order to find feasible solutions.
Compared to the greedy algorithm, 
\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
in the two experiments.
Although the amount is small, it is worth to use \Astar
because optimization methods can help us 
to evaluate the quality of a model 
\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
even an \emph{optimal} sequence can be bad.
If it were not for \Astar, 
we could not tell if the bad result was caused 
by the greedy algorithm or \mine{by} the model.
Because of \Astar, we are sure that the bad result is from
our model of minimizing the 
type change and the compactness.
The ILP-based algorithm finds optimal solutions for some regions,
but for some of the other regions 
it cannot even find a feasible solution.
Compared to the ILP-based algorithm,
\Astar used less memory 
yet found optimal solutions for more regions.

@@

\begin{acks}
We thank Thomas C. van Dijk, Joachim Spoerhase, 
and Sabine Storandt for their valuable suggestions.
We are grateful to Martijn Meijers for 
prereviewing an earlier version of this paper.
\mine{We thank the anonymous reviewers for their comments,
which were very helpful for us to improve the paper.}
\end{acks}
